19Q2

### 2019-06-11 19Q2.Rmd
test sensitivity/resistance annotations on prot HT

```{r load_prot_wilcoxon_rds}
ccle_signif_prot <- readRDS("./data_munging/rds/ccle_signif_protein_changes.rds")
ctrp_signif_prot <- readRDS("./data_munging/rds/ctrp_signif_protein_changes.rds")
gdsc_signif_prot <- readRDS("./data_munging/rds/gdsc_signif_protein_changes.rds")
```

@@

ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
draw(ht_ctrp, heatmap_legend_side = "top")
dev.off()

ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.015)
png(filename = "./plots/manuscript/gdsc_prot_heatmap.png", width = 5, height = 5.5, units = "in", res = 500)
draw(ht_gdsc, heatmap_legend_side = "top")
dev.off()

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot, feature = "protein changes", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.03)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot, feature = "protein changes", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)
# png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 9.5, units = "in", res = 500)
# draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
# dev.off()
```

>>>>

```{r load_prot_wilcoxon_rds}
ccle_signif_prot <- readRDS("./data_munging/rds/ccle_signif_protein_changes.rds")
ccle_signif_prot <- merge(ccle_signif_prot, unique(select(ccle_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)

ctrp_signif_prot <- readRDS("./data_munging/rds/ctrp_signif_protein_changes.rds")
ctrp_signif_prot <- merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)

gdsc_signif_prot <- readRDS("./data_munging/rds/gdsc_signif_protein_changes.rds")
gdsc_signif_prot <- merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
```

@@

ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.015)
png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
draw(ht_ctrp, heatmap_legend_side = "top")
dev.off()

ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.015)
png(filename = "./plots/manuscript/gdsc_prot_heatmap.png", width = 5, height = 5.5, units = "in", res = 500)
draw(ht_gdsc, heatmap_legend_side = "top")
dev.off()
```
